Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/appendix.tex

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
      &=D_n^\Subset(\resultIDE(\transCC_R(P)))\\
      &\subseteq\mvp F(n)\\
      &=\resultIFDS(P)(n)\,.\qedhere
  \end{align*}
\end{proof}

>>>>

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n).
  \end{equation}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\resultIDE(\transCC_R(P))(n')=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\ell\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right)\,.\qedhere
  \end{align*}
\end{proof}
